\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}
\usepackage{parskip}

% Page Geometry
\geometry{left=0.75in, right=0.75in, top=0.75in, bottom=0.75in}

% Section Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}
\titlespacing*{\section}{0pt}{12pt}{6pt}

\begin{document}

\begin{center}
    {\Huge \textbf{Organizer er Taka Nai}} \\
    \vspace{0.2cm}
    Time Limit: 1s \quad Memory Limit: 128MB
\end{center}

\section*{Description}
Seam has officially locked the contest repository. He sits in a state of permanent ``Break,'' refusing to push any new problems to the judge. The organizers are desperate and have started offering him various food items to lure him back to work.

However, Seam is a purist. His taste buds only respond to one specific frequency of chocolate-covered wafer. He will ignore any item, be it \texttt{kacchi}, \texttt{ilish}, or \texttt{burger}; unless it is a \textbf{KitKat}. 

Because Seam's hunger has made his vision blurry, he accepts the word \texttt{kitkat} in any combination of uppercase and lowercase letters (e.g., \texttt{KiTkAt}, \texttt{KITKAT}, and \texttt{kitkat} are all valid). Any other string, even if it contains underscores or different letters, is met with the same fierce ultimatum.

\section*{Input}
The first line contains $t$ ($1 \le t \le 10000$), the number of food items offered to Seam.
The next $t$ lines each contain a string $S$ ($1 \le |S| \le 30$), consisting of uppercase letters, lowercase letters, and underscores (\_).

\section*{Output}
For each food item:
\begin{itemize}
    \item If the string is a case-insensitive match for \texttt{kitkat}, output: \texttt{Problem peye gesi!}
    \item Otherwise, output Seam's ultimatum: \texttt{KITKAT NA KHAWAILE, PROBLEM BANAYE DIMU NA!}
\end{itemize}

\section*{Sample Input / Output}
\begin{table}[h]
\centering
\begin{tabular}{|p{0.45\textwidth}|p{0.45\textwidth}|}
\hline
\textbf{Sample Input} & \textbf{Sample Output} \\ \hline
\texttt{4} \newline \texttt{kacchi\_biryani} \newline \texttt{KiTkAt} \newline \texttt{burger} \newline \texttt{KITKAT} & 
\texttt{KITKAT NA KHAWAILE, PROBLEM BANAYE DIMU NA!} \newline 
\texttt{Problem peye gesi!} \newline 
\texttt{KITKAT NA KHAWAILE, PROBLEM BANAYE DIMU NA!} \newline 
\texttt{Problem peye gesi!} \\ \hline
\end{tabular}
\end{table}

\section*{Formal Editorial: The Case-Insensitive Wafer Theorem}
\textbf{Theorem.} \textit{A setter's acceptance function $A(S)$ is a binary classifier where the positive class is defined by the set $\{s \mid \text{lower}(s) = \text{``kitkat''}\}$.} \\
When the input string $S$ does not belong to the KitKat set, the brain remains in an idle loop. The presence of underscores or non-wafer characters triggers an immediate exception, forcing the setter to broadcast his ultimatum across the network.

\end{document}